\cvsection{Experience}
\begin{cventries}
  \cventry
    {Tech Lead}
    {LearnEnjoy (social utility company)}
    {Paris, France}
    {Jan. 2023 - Mar. 2024}
    {
      \begin{cvitems}
        \item {Technical referent within the company, member of the management committee.}
        \item {"Bien à l'École": technical design and production of educational applications with our EdTech partners.}
        \item {Interoperability: provision of pedagogical applications with the LTI standard.}
        \item {Co-building features and roadmap with the new product team. SCRUM mastering.}
        \item {Recruitment and mentoring within a full stack team of 6 people.}
        \item {Technical stack: Ruby on Rails, Flutter, ExpressJS, Bash, MySQL, Elastic, Redis, Linux, Vagrant, Ansible.}
      \end{cvitems}
      \vspace{-2.0mm}
    }
  \cventry
    {Backend engineer / Devops}
    {}
    {}
    {Dec. 2021 - Jan. 2023}
    {
      \begin{cvitems}
        \item {Development and maintenance of the backoffice dedicated to teachers, healthcare professionals and school heads.}
        \item {Interoperability: provision of pedagogical applications on the French National Education catalog within their GAR portal.}
        \item {Maintenance of development servers and virtual machines.}
        \item {Technical stack: Ruby on Rails, ExpressJS, Bash, MySQL, Elastic, Redis, Linux, Vagrant.}
      \end{cvitems}
    }
  \cventry
    {Lead Developer}
    {Believe Music}
    {Paris, France}
    {June 2020 - Dec. 2021}
    {
      \begin{cvitems}
        \item {Technical referent of "Data Music", a web application exposing music streaming data to artists and label managers.}
        \item {Analysis, retro-documentation, evolution and maintaining of existing application.}
        \item {Step by step transformation of an old monolithic system into a micro-services architecture (API, BFF, micro-apps).}
        \item {Co-building features and roadmap with the product team.}
        \item {Recruiting and mentoring in a full stack team of 9 people.}
        \item {Technical stack: PHP, MariaDB, SvelteJS, Java, Docker.}
      \end{cvitems}
      \vspace{-2.0mm}
    }
  \cventry
    {Backend developer}
    {}
    {}
    {Oct. 2018 - June 2020}
    {
      \begin{cvitems}
        \item {Evolution and maintaining of a data ingestion pipeline (+ than 500M of lines per day).}
        \item {Transformation of the old inadequate system into a cloud ETL system (AWS/Azure).}
        \item {Building of APIs allowing to transition between the legacy system and the cloud ETL.}
        \item {Technical stack: PHP, Bash, MariaDB, AWS (Lambda, S3, SQS), Azure (Synapse), Airflow.}
      \end{cvitems}
    }
  \cventry
    {Backend Developer / Devops}
    {Sikana Education (NGO)}
    {Paris, France}
    {Jan. 2016 - May 2018}
    {
      \begin{cvitems}
        %\item {Sikana is an NGO aiming at producing educative videos to share practical knowledge and skills.}
        \item {Development of www.sikana.tv, a platform where educational videos are available for free in 10 languages.}
        \item {Development of factory.sikana.tv, a collaborative platform where volunteers are able to translate and subtitle videos.}
        \item {Virtual machines administration, continuous integration, deployment, and various tasks automation for video production.}
        \item {Management of technical partnerships with other international NGOs to make the content available in disconnected places.}
        \item {Technical stack: PHP (Symfony 2), Python, MariaDB, Vagrant, Puppet, Git, Capistrano, Jenkins.}
      \end{cvitems}
    }
  \cventry
    {Developer}
    {Gfi Informatique}
    {Orléans, France}
    {Sept. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Conception and development of PHP applications for the customers Thalès Air Systems and GLI biométrie.}
      \end{cvitems}
    }
  \cventry
    {Web Developer (study contract, then full time contract)}
    {Easyflyer (Cimpress group)}
    {Orléans, France}
    {Nov. 2013 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Full stack development of \href{https://www.easyflyer.fr}{easyflyer.fr}, \href{https://www.invite1chef.com}{invite1chef.com}, and kwikydeco.com e-commerce websites with Magento framework.}
        %\item {Integrated API from providers.}
        %\item {Developed invite1chef.com e-commerce website (front and back office) using Magento platform.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{Easyflyer.fr}{Nov. 2013 - Nov. 2014}{}
      %  \cvsubentry{}{Invite1chef.com}{Nov. 2014 - Aug. 2015}{}
      %\end{cvsubentries}
    }
%%%
%  \cventry
%    {Intern Developer}
%    {BSAI}
%    {Blois, France}
%    {June 2013 - Aug. 2013}
%    {
%      \begin{cvitems}
%        \item {Developed database management tools using Code Igniter framework.}
%      \end{cvitems}
%    }
%%%
\end{cventries}
