\cvsection{Experience}
\begin{cventries}
  \cventry
    {Backend Developer}
    {Sikana Education (NGO)}
    {Paris, France}
    {Jan. 2016 - Today}
    {
      \begin{cvitems}
        %\item {Sikana is an NGO aiming at producing educative videos to share practical knowledge and skills.}
        \item {Developed www.sikana.tv, a platform where educational videos are available for free. (running on Symfony framework)}
        \item {Developed factory.sikana.tv, a collaborative platform where volunteers are able to translate and subtitle videos in 12 languages.}
        \item {Integrated Sikana's external API in partnership with Learning Equality, to make the videos available in refugee camps.}
        \item {In charge of virtual machines administration, Quality Assurance, Continuous Integration, and Deployments.}
      \end{cvitems}
    }
  \cventry
    {Developer}
    {Gfi Informatique}
    {Orléans, France}
    {Sept. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Developed evolutions for a database management PHP application. Customer: Thalès Air Systems.}
        \item {Designed Mali's national healthcare management system. Customer: GLI biométrie.}
      \end{cvitems}
    }
  \cventry
    {Web Developer (study contract, then full time contract)}
    {Easyflyer (Cimpress group)}
    {Orléans, France}
    {Nov. 2013 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Developed easyflyer.fr and invite1chef.com e-commerce websites (front and back office) using Magento platform.}
        %\item {Integrated API from providers.}
        %\item {Developed invite1chef.com e-commerce website (front and back office) using Magento platform.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{Easyflyer.fr}{Nov. 2013 - Nov. 2014}{}
      %  \cvsubentry{}{Invite1chef.com}{Nov. 2014 - Aug. 2015}{}
      %\end{cvsubentries}
    }
  \cventry
    {Intern Developer}
    {BSAI}
    {Blois, France}
    {June 2013 - Aug. 2013}
    {
      \begin{cvitems}
        \item {Developed database management tools using Code Igniter framework.}
      \end{cvitems}
    }
\end{cventries}
